\ \\ \LARGE\bf Speculative Evaluation in Particle Swarm Optimization \thanks{Matthew Gardner, Andrew McNabb, and Kevin Seppi are with the Department of Computer Science, Brigham Young University, 3361 TMCB, Provo, UT 84602 (phone: 801-422-8717; email: \{mjg82,a,k\}@cs.byu.edu).}

### 2010-03-22 honors_thesis/journal_paper/paper.tex

At each iteration of the algorithm, the position $\ppos_t$ and velocity
$\pvel_t$ of each particle $i$ are updated as follows:
\begin{align}
\nonumber
	\pvel_{i,t+1} &=
		\constriction \bigl[ \pvel_t
			+ \pcoeff\pURand_{i,t}\otimes(\pbest_{i,t} - \ppos_{i,t}) \\
\label{eq:velupdate}
			& \quad \quad + \ncoeff\nURand_{i,t}\otimes(\nbest_{i,t} - \ppos_{i,t})
		\bigr] \\
\label{eq:posupdate}
	\ppos_{i,t+1} &= \ppos_{i,t} + \pvel_{i,t+1}
\end{align}
where \( \nURand_{i,t} \) and \( \nURand_{i,t} \) are vectors of independent
and identically distributed random numbers drawn from a uniform
distribution, the \( \otimes \) operator is an element-wise vector
multiplication, $\pbest$ (called personal best) is the best position the
current particle has seen, and $\nbest$ (called neighborhood best) is the best
position the neighbors of the current particle have seen~\cite{bratton-sis07}.  \( \ncoeff \), \(
\pcoeff \), and \( \constriction \) are parameters with prescribed values
required to ensure convergence (2.05, 2.05, and .73,
respectively)~\cite{clerc-tec02}. Note also that we have made the particle identifier $i$
and the time step $t$ or $t+1$ explicit in the subscript and moved other qualifiers,
such as the personal $\pers$ and personal best $\pers*$ qualifiers to the superscript position.
Superscripts can be miss read as exponents, but they are qualifiers throughout this paper.

>>>>

At each iteration of the algorithm, the position $\ppos_t$ and velocity
$\pvel_t$ of each particle $i$ are updated as follows:
\begin{align}
\nonumber
	\pvel_{i,t+1} &=
		\constriction \bigl[ \pvel_t
			+ \pcoeff\pURand_{i,t}\otimes(\pbest_{i,t} - \ppos_{i,t}) \\
\label{eq:velupdate}
			& \quad \quad + \ncoeff\nURand_{i,t}\otimes(\nbest_{i,t} - \ppos_{i,t})
		\bigr] \\
\label{eq:posupdate}
	\ppos_{i,t+1} &= \ppos_{i,t} + \pvel_{i,t+1}
\end{align}
where \( \nURand_{i,t} \) and \( \nURand_{i,t} \) are vectors of independent
and identically distributed random numbers drawn from a uniform
distribution, the \( \otimes \) operator is an element-wise vector
multiplication, $\pbest$ (called personal best) is the best position the
current particle has seen, and $\nbest$ (called neighborhood best) is the best
position the neighbors of the current particle have seen~\cite{bratton-sis07}.  \( \ncoeff \), \(
\pcoeff \), and \( \constriction \) are parameters with prescribed values
required to ensure convergence (2.05, 2.05, and .73,
respectively)~\cite{clerc-tec02}. Note also that we have made the particle identifier $i$
and the time step $t$ or $t+1$ explicit in the subscript and moved other qualifiers,
such as the personal $\pers$ qualifier to the superscript position.
Superscripts can be miss read as exponents, but they are qualifiers throughout this paper.
